TBD

### 2016-10-19 paper.tex
cleaning up first section

\subsection{Measurement Equation}
The observed visibility $d_{pq}$ measured by the baseline formed by antenna $p$ and $q$ can be described as

\begin{equation}
\label{eq:vis_definition}
d_{pq} = g_{p}\conj{g_q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise component. Conjugation is denoted by $\conj{(*)}$. During the course of an actual observation the true value of $g_p$, $g_q$ and $y_{pq}$ are unknown and are the quantities which infact have 
to be estimated.

The real and imaginary components of the thermal noise is normally distributed with a mean of zero and a standard deviation that is equal to [NB - are the real and imaginary parts defined with same sigma?]  
\begin{equation}
\sigma = \frac{\sqrt{2}k_{B}T_{\textrm{sys}}}{A\eta\sqrt{\Delta \nu \tau}}, 
\end{equation}
where $k_B$ is Boltzmann's constant, $T_{\textrm{sys}}$ is equal to the system temperature, $A$ is the effective collecting area of each element in the array, $\eta$ is a dimensionless
efficiency factor, $\Delta \nu$ is the observational bandwidth and $\tau$ is the integration time per visibility.

\subsection{Indexing Functions}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: we can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

>>>>

\subsection{Unpolarized Measurement Equation}
The observed visibility $d_{pq}$ measured by the baseline formed by antenna $p$ and $q$ is described by
\begin{equation}
\label{eq:vis_definition}
d_{pq} = g_{p}\conj{g_q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise component. Eq.~\eqref{eq:vis_definition} is known as the unpolarized measurement equation. Conjugation is denoted by $\conj{(*)}$. The true value of $g_p$, $g_q$ and $y_{pq}$ are of course unknown and is what we try to estimate when we calibrate 
and image.

The real and imaginary components of the thermal noise is normally distributed with a mean of zero and a standard deviation proportional to   
\begin{equation}
\sigma \propto \frac{T_{\textrm{sys}}}{\sqrt{\Delta \nu \tau}}, 
\end{equation}
where $T_{\textrm{sys}}$ is equal to the system temperature, $\Delta \nu$ is the observational bandwidth and $\tau$ is the integration time per visibility.

\subsection{Indexing Functions}
In general there are two ways of indexing the visibilities associated with different baselines. We can use the composite index $pq$, which is the strategy that is followed in Eq.~\eqref{eq:vis_definition},
or we can use a single unique baseline index which we assign in numerical order to each composite index; assuming the composite indexes are placed in standard baseline ordering.
The composite indexes $pq$ are ordered using standard baseline ordering

If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: we can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.
